A 38 Million Year Old Mini-Neptune in the Kepler Field

### 2021-10-12 paper/ms.tex
update ms, and AAS journals submitted

\documentclass[12pt,modern,twocolumn,tighten]{aastex63}
%\documentclass[12pt,twocolumn,tighten,linenumbers]{aastex63}
%\documentclass[12pt,twocolumn,tighten,trackchanges]{aastex63}
\usepackage{amsmath,amstext,amssymb}
\usepackage[T1]{fontenc}
\usepackage{apjfonts}
\usepackage[figure,figure*]{hypcap}
\usepackage{graphics,graphicx}
\usepackage{hyperref}
\usepackage{natbib}
\usepackage[caption=false]{subfig} % for subfloat
\usepackage{enumitem} % for specific spacing of enumerate
\usepackage{epigraph}

@@

%% Reintroduced the \received and \accepted commands from AASTeX v5.2.
%% Add "Submitted to " argument.
\received{---}
\revised{---}
\accepted{---}
\submitjournal{AAS Journals}
\shorttitle{Kepler\,1627}

@@

% 208 words (250 max)
\begin{abstract}
  Kepler\,1627A is a G8V star previously known to host a
  $3.8\,R_\oplus$ mini-Neptune on a 7.2\,day orbit.  The star was
  observed by the Kepler space telescope because it is nearby
  ($d=329\,{\rm pc}$) and it resembles the Sun.  Here we show using
  Gaia kinematics, TESS stellar rotation periods, and spectroscopic
  lithium abundances that Kepler\,1627 is a member of the \clusterage\
  old $\delta$~Lyr cluster.  To our knowledge, this makes
  Kepler\,1627Ab the youngest planet with a precise age yet found by
  the main Kepler mission.  The Kepler photometry shows two
  peculiarities: the average transit profile is asymmetric, and the
  individual transit times might be correlated with the local light curve
  slope.  We discuss possible explanations for each anomaly.  More
  importantly, the $\delta$~Lyr cluster
  is one of $\sim$10$^3$ coeval groups whose properties have been clarified
  by Gaia.  Many other exoplanet hosts are potentially kinematic members
  of these clusters; their candidate memberships can be verified by
  measuring stellar rotation periods in the TESS full frame images.
\end{abstract}

@@

For instance, the ``mini-Neptunes'', thought to be made of metal
cores, silicate mantles \citep{kite_atmosphere_2020}, and extended
hydrogen-dominated atmospheres, are expected to shrink
in size by factors of several over their first $10^8$ years.
Specifically, in the models of \citet{owen_atmospheres_2016} and
\citet{owen_constraining_2020}, the $\approx5\,M_\oplus$ planets start
with sizes of 4--12\,$R_\oplus$ shortly after the time of disk
dispersal ($\lesssim$$10^7$\,years), and shrink to sizes of
2--4\,$R_\oplus$ by 10$^8$ years.  While the majority of this change
is expected to occur within the first few million years after the disk
disperses \citep{ikoma_situ_2012}, stellar
irradiation and internal heat can also power gradual outflows
which, if strong enough, can deplete or entirely strip the atmospheric
envelope \citep{Owen_Wu_2013,ginzburg_corepowered_2018}.
Discovering young planets, measuring their masses, and detecting their
atmospheric outflows are key steps toward testing this paradigm, which
is often invoked to explain the observed radius distribution of mature
exoplanets \citep{Fulton_et_al_2017}.

@@

Matching our young star list against stars observed by Kepler revealed
that Kepler observed a portion of the \cn\ (Stephenson-1; Theia~73).
More specifically, a clustering analysis of the Gaia data by
\citet{KounkelCovey2019} reported that Kepler~1627 (KIC 6184894; KOI
5245; TIC 120105470) is a \cn\ member.  Given the previous statistical
validation of the close-in mini-Neptune Kepler 1627b
\citep{2012ApJS..199...24T,morton_false_2016,thompson_planetary_2018},
we begin by examining the properties of the cluster
(Section~\ref{sec:cluster}).  We find that the $\delta$ Lyr cluster is
\clusterage\ old, and in Section~\ref{sec:stars} show that \sn\ is
both a binary and also a member of the cluster.  Focusing on the
planet (Section~\ref{sec:planet}), we confirm that despite the
existence of the previously unreported M2.5V companion, hereafter
Kepler\,1627B, the planet orbits the G-dwarf primary, Kepler\,1627A.
We also analyze an asymmetry in the average transit profile, and a
possible correlation between the individual transit times and the
local light curve slope.  We conclude by discussing broader
implications for our ability to age-date a larger sample of planets
(Section~\ref{sec:conc}).

@@

\begin{figure}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.48\textwidth]{f1.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
    {\bf Galactic positions  and tangential velocities   of stars in the
    $\delta$\,Lyr cluster.} Points are reported cluster members from
    \citet{KounkelCovey2019}.  The tangential velocities relative to
    \sn\ (bottom row) are computed assuming that every star has the
    same three-dimensional spatial velocity as \sn.  Our analysis
    considers stars (black points) in the spatial and kinematic
    vicinity of Kepler\,1627 (yellow star).  The question of whether
    the other candidate cluster members (gray points) are part of the
    cluster is outside our scope.  The location of the Sun is
    ($\odot$) is shown.
		\label{fig:XYZvtang}
	}
\end{figure}

@@

\begin{figure}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.47\textwidth]{f2.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
    {\bf Kepler's view of the $\delta$~Lyr cluster, shown in equatorial
    	coordinates.} Each black circle
    is a candidate cluster member selected from the catalog of
    \citet{KounkelCovey2019} based on its position and kinematics.  Of
    the \nkinematic\ candidate cluster members, 58 have at least one
    quarter of Kepler data.  TESS has also observed most of the
    cluster, for one to two lunar months to date.
		\label{fig:skychart}
	}
\end{figure}

@@

Figure~\ref{fig:lc} shows the resulting best-fit model in orange (top)
and purple (bottom).  The model parameters and their uncertainties,
given in Table~\ref{tab:posterior}, are broadly consistent with a
mini-Neptune sized planet ($3.82\pm0.16\,R_\oplus$) on a close-in
circular\footnote{ Our transit fitting yields $e<0.48$ at 2-$\sigma$;
the constraints on the eccentricity are not particularly strong.}
orbit around a G8V host star ($0.88 \pm 0.02 R_\odot$).  This best-fit
planet size is consistent with those previously reported by
\citet{morton_false_2016} and \citet{berger_identifying_2018}, and
corrects for the small amount of flux dilution from Kepler\,1627B.

\subsubsection{Transit Asymmetry}
\label{subsec:asymmetry}
The transit fit however is not perfect: the lower panels of
Figure~\ref{fig:lc} show an asymmetric residual in the data relative
to the model: the measured flux is high during the first half of
transit, and low in the second half.  The semi-amplitude of this
deviation is $\approx50\,{\rm ppm}$, which represents a $\approx 3\%$
distortion of the transit depth ($\delta=1759\pm62\,{\rm ppm}$).  Note that
although this asymmetry is within the 2-$\sigma$ model uncertainties, the
model has a jitter term that grows to account for otherwise unmodeled
white noise in the flux.  The significance of the asymmetry is
therefore best assessed in comparison against the intrinsic
out-of-transit scatter in the data ($\approx16\,{\rm ppm}$), not the model uncertainties.  The
lower right panel of Figure~\ref{fig:lc} demonstrates that the scatter during
transit is higher than during all other phases of the planet's orbit.

@@

\begin{figure}[tp]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.49\textwidth]{f6.pdf}
	\end{center}
	\vspace{-0.6cm}
	\caption{
    {\bf Possible evidence for a prograde orbit of Kepler 1627 Ab.} The time of
    each Kepler transit was measured, along with the local slope of
    the light curve.  The two quantities are weakly anti-correlated
    ($\approx$2-$\sigma$), which
    could be explained by starspot crossings during the first
    (second) half of transit inducing a positive (negative) TTV,
    provided that the orbit is prograde \citep{mazeh_time_2015}.  The
    units along the abscissa can be understood by considering that the
    stellar flux changes by $\sim$60\,ppt per half rotation period
    ($\sim$1.3\,days).
		\label{fig:corr}
	}
\end{figure}

The previous analysis by \citet{holczer_transit_2016} did not
find any significant long-term transit timing or duration variations
(TTVs or TDVs) for \sn.  Quantitatively, the mean and standard deviation of the
TTVs and TDVs they measured were $-1.1\pm13.8\,{\rm
min}$ and $-3.3\pm22.1\,{\rm min}$.  In an
earlier analysis however, \citet{holczer_time_2015} studied correlations
between TTVs and local light curve slopes, and for \sn\
found a weak correlation of $-29\pm13\,{\rm min}\,{\rm day}^{-1}$
between the two quantities.  Given the possible connection between such
correlations and the unresolved starspot crossings that we expect to
be present in the data for \sn\ \citep{mazeh_time_2015}, we opted to re-examine the
individual transit times.

@@

\begin{figure}[tp]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.45\textwidth]{f7.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
		{\bf Keck/HIRES radial velocities and MuSCAT3 photometry from the transit of 2021 Aug 7.}
		{\it Top:} 
		The radial velocity jitter across the 15~minute exposures
		($\sigma_{\rm RV}\approx30$\ms) prevented us from detecting the RM
		effect;
		a model including the RM anomaly and a quadratic trend in time to
		fit the spot-induced $\approx$\,$250$\ms\ trend is shown (see
		Appendix~\ref{app:rm}).  Shaded bands show 2-$\sigma$ model
		uncertainties.  
		{\it Middle:} The RV variations are strongly correlated with varying
		emission in the Ca H and K lines.
		{\it Bottom}: The photometric transit depths are consistent across
		the {\it griz} bandpasses. The photometry is binned at 10~minute
		intervals.
		\label{fig:ground}
	}
\end{figure}

@@

As an initial plausibility check, Kepler\,1627B contributes 1\% to 2\%
of the total flux observed in the Kepler aperture.  For the sake of
argument, assume the former value.  The observed transit has a depth
of $\approx$0.18\%.  A 18\% deep eclipse of Kepler\,1627B would
therefore be needed to produce a signal with the appropriate depth.
The shape of the transit signal however requires the impact parameter
to be below 0.77 (2-$\sigma$); the tertiary transiting the secondary
would therefore need to be non-grazing with $R_3/R_2 \approx 0.4$.
This yields a contradiction:  this scenario requires an ingress
and egress phase that each span $\approx$40\% of the transit duration
($\approx 68\,{\rm minutes}$).  The actual measured ingress and egress
duration is $\approx 17\,{\rm minutes}$, a factor of four times too
short.  The combination of Kepler 1627B's brightness, the transit
depth, and the ingress duration therefore disfavor the scenario that
Kepler 1627B might host the transit signal.

@@

Beyond this simple test, a line of evidence that
effectively confirms the planetary interpretation is that the stellar density
implied by the transit duration and orbital period is inconsistent
with an eclipsing body around the M-dwarf companion.  We find
$\rho_\star = 2.00 \pm 0.24\,{\rm g\,cm}^{-3}$, while the
theoretically expected density for Kepler\,1627B is $\approx 4.6\,{\rm
g\,cm}^{-3}$ (Table~\ref{tab:posterior}; \citealt{choi_mesa_2016}).
The transit duration is therefore too long to be explained by a star
eclipsing the M dwarf secondary at $10$-$\sigma$.  While the planet
might hypothetically still orbit a hidden close and bright companion,
this possibility is implausible given {\it i)} the lack of secondary
lines in the HIRES spectra, {\it ii)} the lack of secondary
rotation signals in the Kepler photometry, and {\it iii)} the proximity
of \sn\ to the main cluster isochrone on the Gaia CAMD (Figure~\ref{fig:age}).

@@

A third supporting line of evidence for the planetary interpretation
also exists.  We observed a transit of \pn\ on the
night of 2021 Aug 7 simultaneously with Keck/HIRES and MuSCAT3.  We
scheduled the observations using the ephemeris of
\citet{holczer_transit_2016}.  Although we did not detect the
Rossiter-McLaughlin (RM) anomaly, the multi-band MuSCAT3 light curves
show that the transit is achromatic (Figure~\ref{fig:ground}).
Quantitatively, when we fitted the MuSCAT3
photometry with a model that lets the transit depths vary across each
bandpass, we found {\it griz} depths consistent with the Kepler depth
at 0.6, 0.3, 0.3, and 1.1-$\sigma$ respectively.  Conditioned on the
ephemeris and transit depth from the Kepler data, the MuSCAT3 observations also
suggested a transit duration $17.3\pm4.3\ {\rm minutes}$ shorter than the
Kepler transits.
However, given both the lack of transit duration variations in the Kepler data
and the relatively low signal-to-noise of the MuSCAT3 transit,
further photometric follow-up would be necessary to determine
whether the transit duration is indeed changing.  
For our RM analysis,
the details are discussed in Appendix~\ref{app:rm}.  While the
velocities are marginally more consistent with a prograde or polar
orbit than a retrograde orbit, the spot-corrected exposure-to-exposure
scatter ($\sigma_{\rm RV}\approx 30$\ms) is comparable to the expected
RM anomaly assuming an aligned orbit ($\Delta v_{\rm RM}\approx
20\,{\rm m\,s}^{-1}$).  We are therefore not in a position to claim a
spectroscopic detection of the RM effect, nor to quantify the stellar
obliquity.

@@

\begin{figure*}[tp]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.8\textwidth]{f8.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
		{\bf Radii, orbital periods, and ages of transiting exoplanets}.
    Planets younger than a gigayear with ${\rm \tau}/\sigma_{\tau} >
    3$ are emphasized, where $\tau$ is the age and $\sigma_{\tau}$ is
    its uncertainty.  \pn\ is shown with a star.  The large sizes of
    the youngest transiting planets could be explained by their
    primordial atmospheres not yet having evaporated; direct
    measurements of the atmospheric outflows or planetary masses would
    help to confirm this expectation.  Selection effects may also be
    important.  Parameters are from the NASA Exoplanet Archive (2021
    Sept 15).
		\label{fig:rp_period_age}
	}
\end{figure*}

@@

More immediately, the Kepler data may yet contain additional
information.  For instance, one possible explanation for the transit
asymmetry shown in Figure~\ref{fig:lc} is that of a dusty asymmetric
outflow.  
Dusty outflows are theoretically
expected for young mini-Neptunes, and the amplitude of the observed
asymmetry is also consistent with predictions \citep{wang_dai_2019}.
A second possibility is that the planetary orbit is slightly
misaligned from the stellar spin axis, and tends to transit starspot
groups at favored stellar latitudes.  
This fairly contrived geometry would be needed in order to
explain why the starspot crossings could add up coherently.
Other possibilities including
gravity darkening or TTVs causing the asymmetry are disfavored (see
Appendix~\ref{app:asymmetry}).

@@

Ultimately, the main advance of this work is a precise measurement of
the age of \pn.   This measurement was enabled by identifying the
connection of the star to the \cn\ using Gaia kinematics, and then by
using the Gaia color-absolute magnitude diagram and TESS stellar
rotation periods to verify the cluster's existence.
Table~\ref{tab:v06} enables similar cross-matches for both known and
forthcoming exoplanet systems \citep[{\it
e.g.},][]{guerrero_tess_2021}. Confirming these candidate associations
using independent age indicators is essential because their false
positive rates are not known.  A related path is to identify new
kinematic associations around known exoplanet host stars using
positions and tangential velocities from Gaia, and to verify
these associations with stellar rotation periods and spectroscopy
\citep[{\it e.g.},][]{tofflemire_tess_2021}.  Each approach seems
likely to expand the census of planets with precisely measured ages
over the coming years, which will help in deciphering the early stages
of exoplanet evolution.

@@

\clearpage
\acknowledgements
\raggedbottom

>>>>

%\documentclass[12pt,modern,twocolumn,tighten]{aastex63}
\documentclass[12pt,modern,twocolumn,tighten,linenumbers]{aastex63}
%\documentclass[12pt,twocolumn,tighten,linenumbers]{aastex63}
%\documentclass[12pt,twocolumn,tighten,trackchanges]{aastex63}
\usepackage{amsmath,amstext,amssymb}
\usepackage[T1]{fontenc}
\usepackage{apjfonts}
\usepackage[figure,figure*]{hypcap}
\usepackage{graphics,graphicx}
\usepackage{hyperref}
\usepackage{natbib}
\usepackage[caption=false]{subfig} % for subfloat
\usepackage{enumitem} % for specific spacing of enumerate
\usepackage{epigraph}

@@

%% Reintroduced the \received and \accepted commands from AASTeX v5.2.
%% Add "Submitted to " argument.
\received{2021 Oct 12}
\revised{---}
\accepted{---}
\submitjournal{AAS Journals}
\shorttitle{Kepler\,1627}

@@

% 208 words (250 max)
\begin{abstract}
  Kepler\,1627A is a G8V star previously known to host a
  $3.8\,R_\oplus$ mini-Neptune on a 7.2\,day orbit.  The star was
  observed by the Kepler space telescope because it is nearby
  ($d=329\,{\rm pc}$) and it resembles the Sun.  Here we show using
  Gaia kinematics, TESS stellar rotation periods, and spectroscopic
  lithium abundances that Kepler\,1627 is a member of the \clusterage\
  old $\delta$~Lyr cluster.  To our knowledge, this makes
  Kepler\,1627Ab the youngest planet with a precise age yet found by
  the main Kepler mission.  The Kepler photometry shows two
  peculiarities: the average transit profile is asymmetric, and the
  individual transit times might be correlated with the local light curve
  slope.  We discuss possible explanations for each anomaly.  More
  importantly, the $\delta$~Lyr cluster
  is one of $\sim$10$^3$ coeval groups whose properties have been clarified
  by Gaia.  Many other exoplanet hosts are candidate members
  of these clusters; these memberships can be verified with the
  trifecta of Gaia, TESS, and ground-based spectroscopy.
\end{abstract}

@@

For instance, the ``mini-Neptunes'', thought to be made of metal
cores, silicate mantles \citep{kite_atmosphere_2020}, and extended
hydrogen-dominated atmospheres, are expected to shrink
in size by factors of several over their first $10^8$ years.
Specifically, in the models of \citet{owen_atmospheres_2016} and
\citet{owen_constraining_2020}, the $\approx$$5\,M_\oplus$ planets start
with sizes of 4\,--\,12\,$R_\oplus$ shortly after the time of disk
dispersal ($\lesssim$$10^7$\,years), and shrink to sizes of
2\,--\,4\,$R_\oplus$ by 10$^8$ years.  While the majority of this change
is expected to occur within the first few million years after the disk
disperses \citep{ikoma_situ_2012}, stellar
irradiation and internal heat can also power gradual outflows
which, if strong enough, can deplete or entirely strip the atmosphere \citep{Owen_Wu_2013,ginzburg_corepowered_2018}.
Discovering young planets, measuring their masses, and detecting their
atmospheric outflows are key steps toward testing this paradigm, which
is often invoked to explain the observed radius distribution of mature
exoplanets \citep{Fulton_et_al_2017,van_eylen_asteroseismic_2018}.

@@

Matching our young star list against stars observed by Kepler revealed
that Kepler observed a portion of the \cn\ (Stephenson-1; Theia~73).
More specifically, a clustering analysis of the Gaia data by
\citet{KounkelCovey2019} reported that Kepler~1627 (KIC 6184894; KOI
5245) is a \cn\ member.  Given the previous statistical
validation of the close-in mini-Neptune Kepler 1627b
\citep{2012ApJS..199...24T,morton_false_2016,thompson_planetary_2018},
we begin by scrutinizing the properties of the cluster
(Section~\ref{sec:cluster}).  We find that the $\delta$ Lyr cluster is
\clusterage\ old, and in Section~\ref{sec:stars} show that \sn\ is
both a binary and also a member of the cluster.  Focusing on the
planet (Section~\ref{sec:planet}), we confirm that despite the
existence of the previously unreported M2.5V companion, hereafter
Kepler\,1627B, the planet orbits the G-dwarf primary, Kepler\,1627A.
We also analyze an asymmetry in the average transit profile, and a
possible correlation between the individual transit times and the
local light curve slope.  We conclude by discussing broader
implications for our ability to age-date a larger sample of planets
(Section~\ref{sec:conc}).

@@

\begin{figure*}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.95\textwidth]{f1.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
    {\bf Galactic positions  and tangential velocities   of stars in the
    $\delta$\,Lyr cluster.} Points are reported cluster members from
    \citet{KounkelCovey2019}.  The tangential velocities relative to
    \sn\ (bottom right) are computed assuming that every star has the
    same three-dimensional spatial velocity as \sn.  Our analysis
    considers stars (black points) in the spatial and kinematic
    vicinity of Kepler\,1627 (yellow star).  The question of whether
    the other candidate cluster members (gray points) are part of the
    cluster is outside our scope.  The location of the Sun is
    ($\odot$) is shown.
		\label{fig:XYZvtang}
	}
\end{figure*}

@@

\begin{figure}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.47\textwidth]{f2.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
    {\bf Kepler's view of the $\delta$~Lyr cluster, shown in equatorial
    	coordinates.} Each black circle
    is a candidate cluster member selected based on its position and kinematics (Figure~\ref{fig:XYZvtang}).  Of
    the \nkinematic\ candidate cluster members, 58 have at least one
    quarter of Kepler data.  TESS has also observed most of the
    cluster, for one to two lunar months to date.
		\label{fig:skychart}
	}
\end{figure}

@@

Figure~\ref{fig:lc} shows the resulting best-fit model in orange (top)
and purple (bottom).  The model parameters and their uncertainties,
given in Table~\ref{tab:posterior}, are broadly consistent with a
mini-Neptune sized planet ($3.82\pm0.16\,R_\oplus$) on a close-in
circular\footnote{ Our transit fitting yields $e<0.48$ at 2-$\sigma$;
the constraints on the eccentricity are not particularly strong.}
orbit around a G8V host star ($0.88 \pm 0.02 R_\odot$).  This best-fit
planet size is consistent with those previously reported by
\citet{morton_false_2016} and \citet{berger_2018_radii}, and
corrects for the small amount of flux dilution from Kepler\,1627B.

\subsubsection{Transit Asymmetry}
\label{subsec:asymmetry}
The transit fit however is not perfect: the lower panels of
Figure~\ref{fig:lc} show an asymmetric residual in the data relative
to the model: the measured flux is high during the first half of
transit, and low in the second half.  The semi-amplitude of this
deviation is $\approx50\,{\rm ppm}$, which represents a $\approx 3\%$
distortion of the transit depth ($\delta=1759\pm62\,{\rm ppm}$).  Note that
although this asymmetry is within the 2-$\sigma$ model uncertainties, the
model has a jitter term that grows to account for excess
white noise in the flux.  The significance of the asymmetry is
therefore best assessed in comparison against the intrinsic
out-of-transit scatter in the data ($\approx16\,{\rm ppm}$), not the model uncertainties.  The
lower right panel of Figure~\ref{fig:lc} demonstrates that the scatter during
transit is higher than during all other phases of the planet's orbit.

@@

\begin{figure}[tp]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.49\textwidth]{f6.pdf}
	\end{center}
	\vspace{-0.6cm}
	\caption{
    {\bf Possible evidence for a prograde orbit of Kepler 1627 Ab.} The time of
    each Kepler transit was measured, along with the local slope of
    the light curve.  The two quantities are weakly anti-correlated
    ($\approx$2-$\sigma$), which
    might be caused by starspot crossings during the first
    (second) half of transit inducing a positive (negative) TTV,
    provided that the orbit is prograde \citep{mazeh_time_2015}.  The
    units along the abscissa can be understood by considering that the
    stellar flux changes by $\sim$60\,ppt per half rotation period
    ($\sim$1.3\,days).
		\label{fig:corr}
	}
\end{figure}

The previous analysis by \citet{holczer_transit_2016} did not
find any significant long-term transit timing or duration variations
(TTVs or TDVs) for \sn.  Quantitatively, the mean and standard deviation of the
TTVs and TDVs they measured were $-1.1\pm13.8\,{\rm
min}$ and $-3.3\pm22.1\,{\rm min}$.  In an
earlier analysis however, \citet{holczer_time_2015} studied correlations
between TTVs and local light curve slopes, and for \sn\
found a weak correlation of $-29\pm13\,{\rm min}\,{\rm day}^{-1}$
between the two quantities.  Given the possible connection between such
correlations and the unresolved starspot crossings that we expect to
be present in the \sn\ light curve \citep{mazeh_time_2015}, we opted to re-examine the
individual transit times.

@@

\begin{figure}[tp]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.45\textwidth]{f7.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
		{\bf Keck/HIRES radial velocities and MuSCAT3 photometry from the transit of 2021 Aug 7.}
		{\it Top:} 
		The radial velocity jitter across the 15~minute exposures
		($\sigma_{\rm RV}\approx30$\ms) prevented us from detecting the RM
		effect;
		a model including the RM anomaly and a quadratic trend in time to
		fit the spot-induced $\approx$\,$250$\ms\ trend is shown (see
		Appendix~\ref{app:rm}).  Shaded bands show 2-$\sigma$ model
		uncertainties.  
		{\it Middle:} The RV variations are strongly correlated with varying
		emission in the Ca H and K lines.
		{\it Bottom}: The photometric transit depths are consistent across
		the {\it griz} bandpasses. The photometry is binned at 10~minute
		intervals.
		\label{fig:ground}
	}
\end{figure}
\begin{figure*}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.9\textwidth]{f8.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
		{\bf Radii, orbital periods, and ages of transiting exoplanets}.
		Planets younger than a gigayear with ${\rm \tau}/\sigma_{\tau} >
		3$ are emphasized, where $\tau$ is the age and $\sigma_{\tau}$ is
		its uncertainty.  \pn\ is shown with a star.  The large sizes of
		the youngest transiting planets could be explained by their
		primordial atmospheres not yet having evaporated; direct
		measurements of the atmospheric outflows or planetary masses would
		help to confirm this expectation.  Selection effects may also be
		important.  Parameters are from the NASA Exoplanet Archive (2021
		Sept 15).
		\label{fig:rp_period_age}
	}
\end{figure*}

@@

As an initial plausibility check, Kepler\,1627B contributes 1\% to 2\%
of the total flux observed in the Kepler aperture.  For the sake of
argument, assume the former value.  The observed transit has a depth
of $\approx$0.18\%.  A 18\% deep eclipse of Kepler\,1627B would
therefore be needed to produce a signal with the appropriate depth.
The shape of the transit signal however requires the impact parameter
to be below 0.77 (2-$\sigma$); the tertiary transiting the secondary
would therefore need to be non-grazing with $R_3/R_2 \approx 0.4$.
This yields a contradiction:  this scenario requires an ingress
and egress phase that each span $\approx$40\% of the transit duration
($\approx 68\,{\rm min}$).  The actual measured ingress and egress
duration is $\approx 17\,{\rm min}$, a factor of four times too
short.  The combination of Kepler 1627B's brightness, the transit
depth, and the ingress duration therefore disfavor the scenario that
Kepler 1627B might host the transit signal.

@@

Beyond this simple test, a line of evidence that
effectively confirms the planetary interpretation is that the stellar density
implied by the transit duration and orbital period is inconsistent
with an eclipsing body around the M-dwarf companion.  We find
$\rho_\star = 2.00 \pm 0.24\,{\rm g\,cm}^{-3}$, while the
theoretically expected density for Kepler\,1627B is $\approx 4.6\,{\rm
g\,cm}^{-3}$ (Table~\ref{tab:posterior}; \citealt{choi_mesa_2016}).
The transit duration is therefore too long to be explained by a star
eclipsing the M dwarf secondary at $10$-$\sigma$.  While the planet
might hypothetically still orbit a hidden close and bright companion,
this possibility is implausible given {\it i)} the lack of secondary
lines in the HIRES spectra, {\it ii)} the lack of secondary
rotation signals in the Kepler photometry, and {\it iii)} the proximity
of \sn\ to the \cn\ locus on the Gaia CAMD (Figure~\ref{fig:age}).

@@

A third supporting line of evidence for the planetary interpretation
also exists.  We observed a transit of \pn\ on the
night of 2021 Aug 7 simultaneously with Keck/HIRES and MuSCAT3.  We
scheduled the observations using the ephemeris of
\citet{holczer_transit_2016}.  Although we did not detect the
Rossiter-McLaughlin (RM) anomaly, the multi-band MuSCAT3 light curves
show that the transit is achromatic (Figure~\ref{fig:ground}).
Quantitatively, when we fitted the MuSCAT3
photometry with a model that lets the transit depths vary across each
bandpass, we found {\it griz} depths consistent with the Kepler depth
at 0.6, 0.3, 0.3, and 1.1-$\sigma$ respectively.  Conditioned on the
ephemeris and transit depth from the Kepler data, the MuSCAT3 observations also
suggested a transit duration $17.3\pm4.3\ {\rm min}$ shorter than the
Kepler transits.
However, given both the lack of TDVs in the Kepler data
and the relatively low signal-to-noise of the MuSCAT3 transit,
further photometric follow-up would be necessary to determine
whether the transit duration is indeed changing.  
For our RM analysis,
the details are discussed in Appendix~\ref{app:rm}.  While the
velocities are marginally more consistent with a prograde or polar
orbit than a retrograde orbit, the spot-corrected exposure-to-exposure
scatter ($\sigma_{\rm RV}\approx 30$\ms) is comparable to the expected
RM anomaly assuming an aligned orbit ($\Delta v_{\rm RM}\approx
20\,{\rm m\,s}^{-1}$).  We are therefore not in a position to claim a
spectroscopic detection of the RM effect, nor to quantify the stellar
obliquity.

@@

@@

More immediately, the Kepler data may yet contain additional
information.  For instance, one possible explanation for the transit
asymmetry shown in Figure~\ref{fig:lc} is that of a dusty asymmetric
outflow.  
Dusty outflows are theoretically
expected for young mini-Neptunes, and the amplitude of the observed
asymmetry is consistent with predictions \citep{wang_dai_2019}.
A second possibility is that the planetary orbit is slightly
misaligned from the stellar spin axis, and tends to transit starspot
groups at favored stellar latitudes.  
This geometry would be necessary in order to
explain how the starspot crossings could add up coherently.
Other possibilities including
gravity darkening or TTVs causing the asymmetry are disfavored (see
Appendix~\ref{app:asymmetry}).

@@

Ultimately, the main advance of this work is a precise measurement of
the age of \pn.   This measurement was enabled by identifying the
connection of the star to the \cn\ using Gaia kinematics, and by then 
using the Gaia color-absolute magnitude diagram and TESS stellar
rotation periods to verify the cluster's existence.
Table~\ref{tab:v06} enables similar cross-matches for both known and
forthcoming exoplanet systems \citep[{\it
e.g.},][]{guerrero_tess_2021}. Confirming these candidate associations
using independent age indicators is essential because their false
positive rates are not known.  A related path is to identify new
kinematic associations around known exoplanet host stars using
positions and tangential velocities from Gaia, and to verify
these associations with stellar rotation periods and spectroscopy
\citep[{\it e.g.},][]{tofflemire_tess_2021}.  Each approach seems
likely to expand the census of planets with precisely measured ages
over the coming years, which will help in deciphering the early stages
of exoplanet evolution.

@@

%\clearpage
\acknowledgements
\raggedbottom

The authors are grateful to J{.}~Winn, J{.}~Spake, A{.}~Howard, and
T{.}~David for illuminating discussions and suggestions, and to
R{.}~Kerr for providing us with the \citet{Kerr2021} membership list
prior to its publication.  The authors are also grateful to
K{.}~Collins for helping resolve the scheduling conflict that would
have otherwise prevented the MuSCAT3 observations.
%
L.G.B{.} acknowledges support from a Charlotte Elizabeth Procter
Fellowship from Princeton University, as well as from the TESS GI
Program (NASA grants 80NSSC19K0386 and 80NSSC19K1728) and the
Heising-Simons Foundation (51 Pegasi~b Fellowship).
% programs G011103 and G022117, through 
%
%
Keck/NIRC2 imaging was acquired by program 2015A/N301N2L
(PI: A.~Kraus). % and 2019A/N069 (PI: E.~Petigura).
%
In addition, this paper is based in part on observations made with the
MuSCAT3 instrument, developed by the Astrobiology Center and under
financial support by JSPS KAKENHI (JP18H05439) and JST PRESTO
(JPMJPR1775), at Faulkes Telescope North on Maui, HI, operated by the
Las Cumbres Observatory.
%
This work is partly supported by JSPS KAKENHI Grant Numbers 22000005,
JP15H02063, JP17H04574, JP18H05439, JP18H05442, JST PRESTO Grant
Number JPMJPR1775, the Astrobiology Center of National Institutes of
Natural Sciences (NINS) (Grant Number AB031010).
%
% ACKNOWLEDGE PFS / CAMPANAS.
%
This paper also includes data collected by the TESS mission, which are
publicly available from the Mikulski Archive for Space Telescopes
(MAST).
%
Funding for the TESS mission is provided by NASA's Science Mission
directorate.
%
We thank the TESS Architects (G.~Ricker, R.~Vanderspek, D.~Latham,
S.~Seager, J.~Jenkins) and the many TESS team members for their
efforts to make the mission a continued success.
%
%
%This study was based in part on observations at Cerro Tololo
%Inter-American Observatory at NSF's NOIRLab (NOIRLab Prop{.} ID
%2020A-0146; 2020B-0029 PI: Bouma), which is managed by the
%Association of Universities for Research in Astronomy (AURA) under a
%cooperative agreement with the National Science Foundation.
%
%
Finally, this research has made use of the Keck Observatory Archive (KOA),
which is operated by the W. M. Keck Observatory and the NASA Exoplanet
Science Institute (NExScI), under contract with the National
Aeronautics and Space Administration.  We also thank the Keck
Observatory staff for their support of HIRES and remote observing.  We
recognize the importance that the summit of Maunakea has within the
indigenous Hawaiian community, and are deeply grateful to have the
opportunity to conduct observations from this mountain.
%
% The Digitized Sky Survey was produced at the Space Telescope Science
% Institute under U.S. Government grant NAG W-2166.
% Figure~\ref{fig:scene} is based on photographic data obtained using
% the Oschin Schmidt Telescope on Palomar Mountain.
%
